Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-06-04 MS/ms.Rmd
Started table 1, and started writing general effect size paragraph

All titles and abstracts and full text screening was done by two people (DWAN and ML). Any conflicts or disagreements were resolved by discussion and a concensus on a paper was reached. Out of the 417 papers, 79 full texts were screened and we included a total of 62 for final data extraction. For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Materials*.

@@

>>>>

All title, abstract and full text screening was done by two people (DWAN and ML). Any conflicts or disagreements were resolved by discussion and a concensus on a paper was reached. Out of the 417 papers, 79 full texts were screened and we included a total of 62 for final data extraction. For full details on the search strings used, dates searched, the number of papers found, and our PRISMA flowchart (along with reasons for exclusion at the full text stage) we refer readers to the *Supplementary Materials*.

@@

Meta-analysis requires comparative physiologists to make use of effect sizes that are suitable for answering their specific question. The key features of all effect sizes used in meta-analyses are that they are: 1) statistical parameters that have been placed on a common scale so that they can be compared across studies and 2) that they have some associated measure of precision (i.e., sampling variance)[@Koricheva2013; @Borenstein2009; @Schmid2021]. Effect sizes in comparative physiology are quite variable; they can be the mean difference between two groups (e.g., difference in mean between a control and treatment group - see @WuSeebacher2020), the slope of a regression (e.g., between body size and metabolic rate), a correlation between two variables, or even the raw mean (or variance) itself (e.g., comparing CTmax across species - see @Sunday2014).  In many cases, multiple types of effect sizes might be used depending on the question. For example, studies interested in the effect of temperature on some physiological trait that have measured the trait across studies experimentally manipulating temperature could analyse the mean 'effect' by creating contrast-based effect sizes or by analysing the mean in each temperature treatment. The choice as to which one to use will boil down to the types of data available from primary studies, the specific question of interest and whether studies are observational or experimental in nature. Considering our temperature example above, if we are interested in the magnitude of change between temperature treatments, we may want to use a contrast-based effect size, such as the log response ratio $ln_{RR}$. If we are instead interested in how the mean of some physiological trait changes with tempearture we may instead model the mean itself. In the latter scenerio, so long as all the means are measured in the same units (e.g., ; or can be converted to the same units) then the mean may provide the desired answer to a given question. We provide details on different effect measures and associated sample sizes in Table \@ref(tab:tablea).

```{r tablea, echo = FALSE, tab.cap = "Common effect sizes, associated sampling variances and notes on when they might be used. Note that for log odds ratio a continuity correction is applied (i.e., 0.5) to each proportion. In addition, a correction factor, J (1-3 / ..), is applied to the standardised to correct for small sample effects"}

# I'm just listing a bunch here, but we should think about what we want to include. Here's an example of how we can make a table with all equations. Fun!
names <- c("Mean",
           "Variance",
           "Log Response Ratio",
           "Standardised Mean Difference",
           "Zr (Correlation Coefficient)",
           "Log Odds Ratio")
eqns_yi <- c("X_{i}",
             "\\sigma^2",
             "log \\left( \\frac{X_{1}}{X_{2}} \\right)",
             "\\frac{\\left( X_{1} - X_{2}  \\right)}{sd_{p}}J",
             "\\frac{1}{2} log \\left( \\frac{1+r_{i}}{1-r_{i}} \\right)",
             "log \\left( \\frac{y_{i2}+0.5}{n_{i2} - y_{i2}+0.5} \\right) - log \\left( \\frac{y_{i1}+0.5}{n_{i1} - y_{i1}+0.5} \\right)")
#eqns_vi <- c()

table_fin <- data.frame(names, eqns_yi)

# Note: It is esssential that you be clear that the function 'compose' is exported from the flextable package. That's because purr also has the same function, so it gets messy.
tablea <- flextable(table_fin) %>% 
          flextable::compose(j = "names", part = "header", value = as_paragraph(as_b("Effect Measure"))) %>% 
          flextable::compose(j = "eqns_yi", part = "header", value = as_paragraph(as_b("Definition"))) %>% 
          flextable::compose(j = "eqns_yi", value = as_paragraph(as_equation(eqns_yi))) %>% 
          flextable::width(j = 1, 3) %>% 
          flextable::width(j = 2, 2)

tablea

```
